Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-07 manuscript/manuscript.Rmd
changed hypothesis table in manuscript and talk

```{r setup, include = FALSE}
# devtools::install_github("crsh/papaja@devel")
library(papaja)
library(raincloudplots)
library(ggplot2)
library(broom)
library(purrr)
library(glue)
library(readr)
library(dplyr)
library(rmarkdown)
library(here)
r_refs("r-references.bib")
```

@@

## Table 2
```{r, echo = FALSE}
table2 <- data.frame(
  Measure = c("1. Final beliefs",
              "2. Credibility", 
              "3. Confidence",
              "4. Bias",
              "5. Error",
              "6. Discretion"),
  Multi_Consistent = c("+", "+", "-", "-", "-", "No prediction"),
  Multi_Inconsistent = c("-", "-", "-", "+", "+", "No prediction"))

knitr::kable(table2,
             col.names = c("Measure", 
                           "Many-analyst: Consistent", 
                           "Many-analyst: Inconsistent"),
             align = "lcc",
             label = NA,
             caption = "Predicted direction of effects for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs")
```
*Note*. Table 2 indicates the predicted direction of the effect for each of the five dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.  
\newpage

>>>>

```{r setup, include = FALSE}
# devtools::install_github("crsh/papaja@devel")
library(papaja)
library(raincloudplots)
library(ggplot2)
library(broom)
library(purrr)
library(glue)
library(readr)
library(dplyr)
library(rmarkdown)
library(here)
library(icons)
library(rsvg)
r_refs("r-references.bib")
```

@@

## Table 2

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| 1. Posterior beliefs | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
|2. Credibility | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` |
| 3. Confidence  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`  | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | 
| 4. Bias | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 5. Error | `r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")` | `r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")` |
| 6. Discretion | No prediction | No prediction |
*Note*. Table 2 indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs (a green plus stands for a positive prediction, and a red minus stands for a negative prediction). For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.  
\newpage

### 2021-10-07 talk/index.Rmd
talk: hypotheses
added artwork
changed hypothesis table in manuscript and talk

---
# Open Science Statement

@@

@@

We run an experiment with **three conditions**:
--

@@

.pull-left[
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Posterior beliefs  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceptions of credibility  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Confidence in the aggregate effect size estimate  
]
.pull-right[
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of bias  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of error  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of degrees of freedom  
]

>>>>

---
background-image: url("https://github.com/allisonhorst/stats-illustrations/raw/master/rstats-artwork/reproducibility_court.png")
background-position: 90% 50%
background-size: 50%

@@

.right[
Artwork by [@allison_horst](https://github.com/allisonhorst/stats-illustrations)
]

@@

We run an experiment with **three conditions**
--

@@

.pull-left[
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Posterior beliefs  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Perceptions of credibility  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Confidence in the aggregate effect size estimate  
]
.pull-right[
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of bias  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of error  
`r icon_style(icons::fontawesome("angle-right"), scale = 1.5, fill = "#035AA6")` Ratings of discretion  
]

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
| Error | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

---
.center[

# Hypotheses

`r icon_style(icons::fontawesome("compass"), scale = 1.5, fill = "#035AA6")` $~~~~$**Predicted direction of effects**

`r icon_style(icons::fontawesome("users-slash"), scale = 1.5, fill = "#035AA6")` $~~~$**Compared to the single-analyst condition**

`r icon_style(icons::fontawesome("history"), scale = 1.5, fill = "#035AA6")` $~~~~$**Controlling for prior beliefs**

| Measure | Multi-consistent | Multi-inconsistent |
| ------------- |  ------------- | ------------- | 
| Posterior beliefs | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
|Credibility | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] |
| Confidence  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`]  | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | 
| Bias | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
| Error | .center[`r icon_style(icons::fontawesome("user-minus"), scale = 1.5, fill = "red")`] | .center[`r icon_style(icons::fontawesome("user-plus"), scale = 1.5, fill = "green")`] |
| Discretion | .center[No prediction] | .center[No prediction] |
]

*Note*. Table indicates the predicted direction of the effect for all dependent variables, compared to the single-analyst condition and controlling for prior beliefs. For example, we hypothesized that, compared to a single-analyst study and controlling for prior beliefs,  ratings of credibility would be greater in the multi-analyst: consistent condition and lower in the multi-analyst: inconsistent condition.

# Survey Materials
